\textsf{Are large language models superhuman chemists?}

### 2024-10-18 src/tex/appendix.tex
escape more

        \textbf{Question Type} & \textbf{\%} & \textbf{Example Questions}  \\ 

@@

        Organic Chemistry & 15.5 & What is the reaction mechanism that describes the following reaction (represented using reaction SMILES) [START_RXNSMILES]CCCl.CO[Na]>>[Na]Cl.CCOC[END_RXNSMILES]? \\

@@

        Materials Science & 3.1 & For NMR analysis, you need to digest the MOF in a strong acid to remove the linker and leave the metal clusters intact. Why would one choose \\ce{HF} over \\ce{HCl} for this purpose? \\
        & & A. \\ce{F-} forms a stable bonds to the metal ions \\
        & & B. \\ce{HF} has a better water solubility than \\ce{HCl} \\
        & & C. \\ce{HF} has a higher boiling point than \\ce{HCl} \\
        & & D. \\ce{HF} is a weaker acid than \\ce{HCl} \\

@@

        & & A. \\ce{NH4Cl} \\
        & & B. \\ce{Na2CO3} \\
        & & C. \\ce{NaH2PO4} \\
        & & D. \\ce{Zn(OH)Cl} \\

@@

        & & A. \\ce{C60} \\
        & & B. \\ce{CH4} \\
        & & C. \\ce{Fe(CO)5} \\
        & & D. \\ce{H2+} \\
        & & E. \\ce{NaCl} \\

@@

        Inorganic Chemistry & 3.3 & What is the oxidation number of the metal in the compound \\ce{[ZrF7]^{3-}}\\

@@

\begin{table*}[!t]
    \centering
        \caption{Examples for each of the required skills considered in the \chembench corpus.}
    \begin{tabular}{p{2.7cm}cp{10cm}}
        \toprule
        \textbf{Required skills} & \textbf{Number of Questions} & \textbf{Example Question} \\
        \midrule
        Knowledge & 770 & Which of the following salts is an acidic salt? \\
        & & A. \\ce{NH4Cl} \\
        & & B. \\ce{Na2CO3} \\
        & & C. \\ce{NaH2PO4} \\
        & & D. \\ce{Zn(OH)Cl} \\
        \midrule
        Reasoning & 825 & How can the optical impact of quantum confinement on the electronic structure of a quantum dot be observed experimentally? \\
        & & A. By measuring atomic force microscopy \\
        & & B. By measuring fourier transform infrared spectroscopy \\
        & & C. By measuring photoluminescence spectrum \\
        & & D. By measuring the absorption spectroscopy \\
        \midrule
        Intuition & 1001 & Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
        & & A. [START_SMILES]CC1(C)Oc2ccc([N+](=O)[O-])cc2[C@@H](N2CCOCC2)[C@@H]1O[END_SMILES] \\
        & & B. [START_SMILES]Cc1ccccc1N=C(S)N1CCC(NC(=O)c2ccco2)CC1[END_SMILES] \\
        \midrule
        Calculation & 91 & Given that the average molar mass of the polymer chains in this sample of poly(lactic acid) (PLA) is \\pu{595 g mol^{-1}} using end-group analysis, where \\pu{0.1619 g} of PLA was dissolved in \\pu{25 cm^3} of benzyl alcohol and titrated with \\pu{0.0400 mol dm^{-3}} \\ce{KOH} solution. The volume of \\ce{KOH} solution required to reach the endpoint was \\pu{6.81 cm^3}. What is the average number of monomer units in each polymer chain of this sample? \\
        \bottomrule
    \end{tabular}
    \label{tab:chembench_corpus_cognitive}
\end{table*}

>>>>

        Question Type & \% & Example Questions  \\ 

@@

        Organic Chemistry & 15.5 & What is the reaction mechanism that describes the following reaction (represented using reaction SMILES) [START\_RXNSMILES]CCCl.CO[Na]>>[Na]Cl.CCOC[END\_RXNSMILES]? \\

@@

        Materials Science & 3.1 & For NMR analysis, you need to digest the MOF in a strong acid to remove the linker and leave the metal clusters intact. Why would one choose \ce{HF} over \ce{HCl} for this purpose? \\
        & & A. \ce{F-} forms a stable bonds to the metal ions \\
        & & B. \ce{HF} has a better water solubility than \ce{HCl} \\
        & & C. \ce{HF} has a higher boiling point than \ce{HCl} \\
        & & D. \ce{HF} is a weaker acid than \ce{HCl} \\

@@

        & & A. \ce{NH4Cl} \\
        & & B. \ce{Na2CO3} \\
        & & C. \ce{NaH2PO4} \\
        & & D. \ce{Zn(OH)Cl} \\

@@

        & & A. \ce{C60} \\
        & & B. \ce{CH4} \\
        & & C. \ce{Fe(CO)5} \\
        & & D. \ce{H2+} \\
        & & E. \ce{NaCl} \\

@@

        Inorganic Chemistry & 3.3 & What is the oxidation number of the metal in the compound \ce{[ZrF7]^{3-}}\\

@@

\begin{table*}[!t]
    \centering
        \caption{Examples for each of the required skills considered in the \chembench corpus.}
    \begin{tabular}{p{2.7cm}cp{10cm}}
        \toprule
        Required Skills & Number of Questions & Example Question \\
        \midrule
        Knowledge & 770 & Which of the following salts is an acidic salt? \\
        & & A. \ce{NH4Cl} \\
        & & B. \ce{Na2CO3} \\
        & & C. \ce{NaH2PO4} \\
        & & D. \ce{Zn(OH)Cl} \\
        \midrule
        Reasoning & 825 & How can the optical impact of quantum confinement on the electronic structure of a quantum dot be observed experimentally? \\
        & & A. By measuring atomic force microscopy \\
        & & B. By measuring fourier transform infrared spectroscopy \\
        & & C. By measuring photoluminescence spectrum \\
        & & D. By measuring the absorption spectroscopy \\
        \midrule
        Intuition & 1001 & Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
        & & A. [START\_SMILES]CC1(C)Oc2ccc([N+](=O)[O-])cc2[C@@H](N2CCOCC2)[C\@\@H]1O[END\_SMILES] \\
        & & B. [START\_SMILES]Cc1ccccc1N=C(S)N1CCC(NC(=O)c2ccco2)CC1[END\_SMILES] \\
        \midrule
        Calculation & 91 & Given that the average molar mass of the polymer chains in this sample of poly(lactic acid) (PLA) is \pu{595 g mol^{-1}} using end-group analysis, where \pu{0.1619 g} of PLA was dissolved in \pu{25 cm^3} of benzyl alcohol and titrated with \pu{0.0400 mol dm^{-3}} \ce{KOH} solution. The volume of \ce{KOH} solution required to reach the endpoint was \pu{6.81 cm^3}. What is the average number of monomer units in each polymer chain of this sample? \\
        \bottomrule
    \end{tabular}
    \label{tab:chembench_corpus_cognitive}
\end{table*}
